Supplementary Material

### 2023-04-26 3 Analysis Scripts/StatiscalAnalysis_ModelFitting.qmd
continue work on manuscript, supplement, cv

data %>% 
  ggplot(aes(x = samp, y = Burden)) + 
  geom_point() + 
  geom_line() +
  facet_wrap(~ nes) 
```

@@

plot(compare_performance(glmer_fit_null,glmer_fit_global, glmer_fit_1, glmer_fit_2, glmer_fit_3, glmer_fit_4, glmer_fit_5, glmer_fit_6, glmer_fit_7, glmer_fit_8, glmer_fit_9, glmer_fit_10, glmer_fit_11, glmer_fit_12))
```

@@

```{r}
check_model(glmer_fit_11)

@@

MLp <- plot_model(glmer_fit_11,terms = 's.lui', type="pred", 
           show.data = TRUE, show.values = TRUE, show.p = TRUE,
           title = "", show.legend = TRUE, line.size=1,
           axis.title = c("Landfill Use Index",'Multi-Drug Resistence'))

##Not working... fix later
  while (!is.null(dev.list()))  dev.off()
#Tiff 
tiff(file = here('5 Manuscript','manuscript','Images', 'LUIvsMDR_LME.tiff'))
MLp
dev.off() 
```

@@

plot(compare_performance(lmer_fit2_null, lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8,
                                  lmer_fit2_9, lmer_fit2_10, lmer_fit2_11, lmer_fit2_12))
```

@@

```{r}
check_model(lmer_fit2_5)

>>>>

facet_plot <- data %>% 
  ggplot(aes(x = samp, y = Burden)) + 
  geom_point() + 
  geom_line() +
  facet_wrap(~ nes) 
facet_plot

png(file = here('5 Manuscript','manuscript','supplement', 'Supplementary_Material_files', 'facet_plot.png'))
facet_plot
dev.off() 
```

@@

glmer_indices <- plot(compare_performance(glmer_fit_null,glmer_fit_global, glmer_fit_1, glmer_fit_2, glmer_fit_3, glmer_fit_4, glmer_fit_5, glmer_fit_6, glmer_fit_7, glmer_fit_8, glmer_fit_9, glmer_fit_10, glmer_fit_11, glmer_fit_12))

#Tiff 
png(file = here('5 Manuscript','manuscript','supplement', 'Supplementary_Material_files', 'glmer_indices.png'))
glmer_indices
dev.off() 
```

@@

```{r}
glmer_check <- check_model(glmer_fit_11)

png(file = here('5 Manuscript','manuscript','supplement', 'Supplementary_Material_files', 'glmer_check.png'))
glmer_check
dev.off()

@@

MLp <- plot_model(glmer_fit_11,terms = 's.lui', type="pred", 
           show.data = TRUE, show.values = TRUE, show.p = TRUE,
           title = "", show.legend = TRUE, line.size=1,
           axis.title = c("Landfill Use Index",'Multi-Drug Resistence'))
##Not working... fix later
  while (!is.null(dev.list()))  dev.off()
#Tiff 
tiff(file = here('5 Manuscript','manuscript','Images', 'LUIvsMDR_LME.tiff'))
MLp
dev.off() 
```

@@

lmer_indices <-plot(compare_performance(lmer_fit2_null, lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8, lmer_fit2_9, lmer_fit2_10, lmer_fit2_11, lmer_fit2_12))

plot(compare_performance(lmer_fit2_null, lmer_fit2_global, lmer_fit2_1, lmer_fit2_2, lmer_fit2_3, lmer_fit2_4, lmer_fit2_5, lmer_fit2_6, lmer_fit2_7, lmer_fit2_8, lmer_fit2_9, lmer_fit2_10, lmer_fit2_11, lmer_fit2_12))

png(file = here('5 Manuscript','manuscript','supplement', 'Supplementary_Material_files', 'lmer_indices.png'))
lmer_indices
dev.off()

@@

```{r}
lmer_check <- check_model(glmer_fit_global)
lmer_check

png(file = here('5 Manuscript','manuscript','supplement', 'Supplementary_Material_files', 'lmer_check.png'))
lmer_check
dev.off()

### 2023-04-26 3 Analysis Scripts/crossvalidation.qmd
continue work on manuscript, supplement, cv

#path to data
data_location <- here::here("2 Clean Data","stork_AMR_2021.rds")

@@

```{r}
# 5-fold cross-validation, 5 times repeated, using MDR as strata 
folds <- vfold_cv(train_data, v = 5, repeats = 5, strata = as.factor(MDR))

@@

#create recipes for each model

null_mod <-

#create tree workflow
tree_workflow <- workflow() %>%
  add_model(tree_model) %>%
  add_formula(as.factor(MDR) ~ .)
```

```{r}
glmertree_global <- glmertree::glmertree(as.factor(MDR) ~ 1|nes| + s.lui + s.age + samp + s.nsuccess, 
                                         data = train_data, family = "binomial")
plot(glmertree_global)
```

>>>>

#path to data
data_location <- here::here("2 Clean Data","stork_AMR_clean.rds")

@@

```{r}
# 5-fold cross-validation, 5 times repeated, using MDR as strata 
folds <- vfold_cv(train_data, v = 5, repeats = 5, strata = MDR)

@@

#create tree workflow for global model
tree_workflow_global <- workflow() %>%
  add_model(tree_model) %>%
  add_formula(Burden ~ s.lui + s.age + samp + s.nsuccess + nes)

#tree grid
tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          levels = 5)

#tree_resamples
tree_resamp <- 
  tree_workflow_global %>% 
  tune_grid(
    resamples = folds,
    grid = tree_grid
    )

tree_resamp %>%
  collect_metrics()

tree_resamp %>%
  autoplot()
```
```{r}
#create tree workflow for null
tree_workflow_null <- workflow() %>%
  add_model(tree_model) %>%
  add_formula(Burden ~ 1)

#tree_resamples
tree_resamp_null <- 
  tree_workflow_null %>% 
  tune_grid(
    resamples = folds,
    grid = tree_grid
    )

tree_resamp_null %>%
  collect_metrics()

tree_resamp_null %>%
  autoplot()
```

### 2023-04-26 5 Manuscript/manuscript/supplement/Supplementary_Material.qmd
continue work on manuscript, supplement, cv

---
title: "Supplementary Material"
subtitle: "A Match Made in Landfills? Exploring the diversity and burden of antimicrobial resistance genes carried by white stork (Ciconia ciconia) throughout the breeding season in Madrid, Spain"
author: Raquel Francisco and Seth Lattner
date: "`r Sys.Date()`"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: EW_AMR.bib
csl: ../../vancouver.csl
---

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```

@@

Contained in this document is supplementary material for **"A Match Made in Landfills? Exploring the diversity and burden of antimicrobial resistance genes carried by white stork (*Ciconia ciconia*) throughout the breeding season in Madrid, Spain"**. Supplementary materials include instructions for reproducing data analysis, model results, and any additional analysis.

@@

Show additional results here. Those can be some useful exploratory/descriptive figures or tables, or results from additional analyses that didn't make it into the main text.

## Example additional result

@tbl-resulttable1 shows an additional table summarizing a model fit.

```{r}
#| label: tbl-resulttable1
#| tbl-cap: "Another fit table."
#| echo: FALSE
resulttable1 = readRDS(here("results","resulttable1.rds"))
knitr::kable(resulttable1)
```

@fig-result2 shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result2
#| fig-cap: "Height and weight."
#| echo: FALSE
knitr::include_graphics(here("results","height_weight.png"))
```

>>>>

---
title: "Supplementary Material"
subtitle: "A Match Made in Landfills? Exploring the diversity and burden of antimicrobial resistance genes carried by white stork (Ciconia ciconia) throughout the breeding season in Madrid, Spain"
author: Raquel Francisco and Seth Lattner
date: "`r Sys.Date()`"
format: html
editor: visual
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# load a few R packages
library(here)
library(knitr)
```

@@

Contained in this document is supplementary material for the manuscript, **"A Match Made in Landfills? Exploring the diversity and burden of antimicrobial resistance genes carried by white stork (*Ciconia ciconia*) throughout the breeding season in Madrid, Spain"**. Supplementary materials include instructions for reproducing data analysis and additonal model results.

@@

## Exploratory Analysis Results

## Full Analysis Results

A total of 14 GLMMs (including a global and null model) were run to assess the effects of several predictors on MDR. Based on Akaike's Information Criterion adjusted for small sample size (AIC*c*), model 11 (containing the predictors LUI and age) was the highest performing model. A total of 15 LMMs were run to assess the effects of several predictors on AMR. Based on AIC*c*, the global model was the highest performing model, followed by a univariate LMM containing age as the only predictor.

![Figure 1. Facet Plot of single factor repeated measures evaluation the effect of LUI on blaTEM (betalactam) resistence gene burden](Supplementary_Material_files/facet_plot.png)

### GLMM Model Results

![Figure 2. Comparison of Generalized Linear Mixed Model Indices](Supplementary_Material_files/glmer_indices.png)

![Figure 3. Model Check Metrics for Best-performing GLMM](Supplementary_Material_files/glmer_check.png)

### LMM Model Results

![Figure 4. Comparison of Linear Mixed Model Indices](Supplementary_Material_files/lmer_indices.png)
![Figure 5. Model Check Metrics for Best-performing LMM](Supplementary_Material_files/lmer_check.png)
